### 2019-04-16 Thesis/games.tex
Finished chapter.

  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $L_A$ for the set of legal sequences occurring in $A$.
\end{definition}

@@

\begin{definition}
  Given a legal sequence $s\in L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.

@@

  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\times B$ by
  \begin{itemize}
    \item $M_{A\times B} = M_A + M_B$,
    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\times B} = \{s\in L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
  \end{itemize}
  We extend this to arbitrary products $\prod_i A_i$ in the obvious way.
  In particular, the product $1$ of the empty collection is the same as the empty game $I$ defined in Example \ref{ExEmptyGame}.
  \label{DefProduct}
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\tensor B$ by
  \begin{itemize}
    \item $M_{A\tensor B} = M_A + M_B$,
    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\tensor B} = \{s\in L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\implies B$ by
  \begin{itemize}
    \item $M_{A\implies B} = M_A + M_B$,
    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$,
    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
    \item $P_{A\implies B} = \{s\in L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Given a game $A$, define a game $\oc A$ by
  \begin{itemize}
    \item $M_{\oc A}=M_A$,
    \item $\lambda_{\oc A} = \lambda_A$,
    \item $\ts_{\oc A} = \ts_A$ and
    \item $P_{\oc A} = \{s\in L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Let $A,B,C$ be arenas.  
  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in L_{A\implies B}$ and $\s\vert_{B,C}\in L_{B\implies C}$.  
  Here, $\s\vert_{A,B}$ is the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$, together with all justification pointers between moves in $A$ and $B$, and $\s\vert_{B,C}$ is defined similarly.

@@

  ii) If $bs$ ends with a $P$-move in $A$, then $\ov{bs}_{A\implies B} = b\pv{s\vert_A}^A$.
  \label{LemProjectionLemma}
\end{lemma}
\begin{proof}
  Induction on the length of $s$.
  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\pv{b}^{A\implies B} = b = \pv{b}^{B}$.

@@

\begin{proposition}
  $\sigma;\tau$ is a strategy for $A\implies C$.  
\end{proposition}
\begin{proof}
  First, we claim that $\s\vert_{A,C}\in P_{A\implies B}$ for any $\s\in \sigma\|\tau$.
  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in L_{A\implies C}$.

@@

  Lastly, we need to show that $\s\vert_{A,C}$ satisfies the visibility condition.
  Let $ta\prefix\s\vert_{A,C}$.
  Choose some $\t\prefix\s$ such that $\t\vert_{A,C}=t$.

  Suppose $a$ is a $P$-move.
  Then by Lemma \ref{LemHarmersLemma}, $\pv{\t a}\in\Int(A,B,C)$.  
  By Lemma \ref{LemHarmerRestriction}, $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.

  Secondly, suppose that $a$ is an $O$-move.
  If $a$ is an $O$-move in $C$, then either it is initial or $t$ ends with some $P$-move in $B$, and therefore $\ov{t}_{A\implies C}=\ov{t\vert_B}_B = \ov{\t\vert_{B,C}}_B$.  
  Therefore, since $t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
  If $a$ is an $O$-move in $A$, then write $t=cu$ and $\t=c\u$, where $c$ is the starting move in $C$.
  We have $\ov{cua}_{A\implies C}=c\pv{u\vert_A a}^A = \ov{c\u\vert_{A,B}}_{A\implies B}$.  
  Therefore, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.

  Therefore, $\s\vert_{A,C}\in L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.

@@

In this section, we shall prove that composition of strategies is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.  
To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in L_{A\implies B}$, $\u\vert_{B,C}\in L_{B\implies C}$ and $\u\vert_{C,D}\in L_{C \implies D}$.  
Given such a sequence $\u$, we define $\u\vert_{A,D}$ as before; i.e., we take all moves from $\u$ occurring in $A$ and $D$, together with justification pointers within these games, and if an initial move in $A$ is justified by an initial move in $B$, which is justified by an initial move in $C$, which is justified by an initial move in $D$, then we add a justification pointer from that move in $A$ to that move in $D$.

@@

\begin{definition}[\cite{laird02}]
  A \emph{sequoidal category} $\C$ is given by
  \begin{itemize}
    \item a symmetric monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,$ $\lunit$, $\runit$, $\sym$);
    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
      \begin{mathpar}
        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
        \and
        \run_a \from a \toisom a \sequoid I
      \end{mathpar}
      that make the diagrams
      \begin{mathpar}
        \begin{tikzcd}[column sep=31pt]
          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
            & a \sequoid (x \tensor (y \tensor z))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
            & a \sequoid (I \tensor x) \\
          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
            &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
            & a \sequoid (x \tensor I) \\
          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
      commute; and
    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
      \begin{mathpar}
        \begin{tikzcd}[column sep=30pt]
          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
            & J(a \sequoid (x \tensor y))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
            & J(a \sequoid I) \\
          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
  \end{itemize}
  \label{DefSequoidalCategory}
\end{definition}
\begin{remark}
  The definitions of \emph{lax action} can be found at the start of chapter \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.  
  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in chapter \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.  
  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
\end{remark}

@@

Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
\[
  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
  \]
Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
In other words, by Proposition \ref{PropFormulaForAlpha}, $\rread$ is the composite
\[
  \rread = \oc\bN \xrightarrow{\mu_\bN} \oc\bN \tensor \oc\bN \xrightarrow{\der_\bN\tensor\oc\bN} \bN \tensor \oc\bN \xrightarrow{\wk_{\bN,\oc\bN}} \bN \sequoid\oc\bN\,.
  \]
Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
\[
  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
  \]
We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
\[
  \begin{tikzcd}
    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
      & \Varr \sequoid \oc\Varr
  \end{tikzcd}
  \]
Concretely, the strategy $\cell$ behaves as follows.  
When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.

@@

@@

Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$ and $\V_\Gamma$ for $\Varr \times \cdots \times \Varr$, where in each case the terms of the tensor product are indexed by the variables in $\Gamma$.  
Then, given some term $\Gamma\ts M$ in context, its denotation will be a morphism $\deno{\Gamma\ts M\from T} \from \oc \V_\Gamma \implies \deno{T}$.

>>>>

  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $\L_A$ for the set of legal sequences occurring in $A$.
\end{definition}

@@

\begin{definition}
  Given a legal sequence $s\in \L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.

@@

  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\times B$ by
  \begin{itemize}
    \item $M_{A\times B} = M_A + M_B$,
    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\times B} = \{s\in \L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
  \end{itemize}
  We extend this to arbitrary products $\prod_i A_i$ in the obvious way.
  In particular, the product $1$ of the empty collection is the same as the empty game $I$ defined in Example \ref{ExEmptyGame}.
  \label{DefProduct}
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\tensor B$ by
  \begin{itemize}
    \item $M_{A\tensor B} = M_A + M_B$,
    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\tensor B} = \{s\in \L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Given games $A$,$B$, define a game $A\implies B$ by
  \begin{itemize}
    \item $M_{A\implies B} = M_A + M_B$,
    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$,
    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
    \item $P_{A\implies B} = \{s\in \L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Given a game $A$, define a game $\oc A$ by
  \begin{itemize}
    \item $M_{\oc A}=M_A$,
    \item $\lambda_{\oc A} = \lambda_A$,
    \item $\ts_{\oc A} = \ts_A$ and
    \item $P_{\oc A} = \{s\in \L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
  \end{itemize}
\end{definition}

@@

\begin{definition}
  Let $A,B,C$ be arenas.  
  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in \L_{A\implies B}$ and $\s\vert_{B,C}\in \L_{B\implies C}$.  
  Here, $\s\vert_{A,B}$ is the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$, together with all justification pointers between moves in $A$ and $B$, and $\s\vert_{B,C}$ is defined similarly.

@@

  ii) If $bs$ ends with a $P$-move in $A$, then $\ov{bs}_{A\implies B} = b\pv{s\vert_A}^A$.
  \label{LemProjectionLemma}
\end{lemma}
\begin{proof}
  Induction on the length of $s$.
  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\ov{b}^{A\implies B} = b = \ov{b}^{B}$.

@@

\begin{proposition}
  $\sigma;\tau$ is a strategy for $A\implies C$.  
  \label{PropComposition}
\end{proposition}
\begin{proof}
  First, we claim that $\s\vert_{A,C}\in P_{A\implies B}$ for any $\s\in \sigma\|\tau$.
  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in \L_{A\implies C}$.

@@

  Lastly, we need to show that $\s\vert_{A,C}$ satisfies the visibility condition.
  Let $ta\prefix\s\vert_{A,C}$.
  Choose some $\t a\prefix\s$ such that $\t a\vert_{A,C}=ta$.

  Suppose $a$ is a $P$-move.
  Then by Lemma \ref{LemHarmersLemma}, $\pv{\t a}\in\Int(A,B,C)$.  
  By Lemma \ref{LemHarmerRestriction}, we know that $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.

  Secondly, suppose that $a$ is an $O$-move.
  If $a$ is an $O$-move in $C$, then either it is initial or $\t$ ends with some $P$-move in $C$, and therefore $\ov{t}_{A\implies C} = \ov{t\vert_C}_C = \ov{\t\vert_{B,C}}_C$ by Lemma \ref{LemProjectionLemma}.
  Therefore, since $\t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
  If $a$ is an $O$-move in $A$, then write $t=cu$ and $\t=c\u$, where $c$ is the starting move in $C$.
  We have $\ov{cua}_{A\implies C}=c\pv{u\vert_A a}^A = \ov{c\u\vert_{A,B}}_{A\implies B}$.  
  Therefore, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.

  Therefore, $\s\vert_{A,C}\in \L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.

@@

In this section, we shall prove that composition of strategies is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.  
To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in \L_{A\implies B}$, $\u\vert_{B,C}\in \L_{B\implies C}$ and $\u\vert_{C,D}\in \L_{C \implies D}$.  
Given such a sequence $\u$, we define $\u\vert_{A,D}$ as before; i.e., we take all moves from $\u$ occurring in $A$ and $D$, together with justification pointers within these games, and if an initial move in $A$ is justified by an initial move in $B$, which is justified by an initial move in $C$, which is justified by an initial move in $D$, then we add a justification pointer from that move in $A$ to that move in $D$.

@@

\begin{definition}[\cite{laird02}]
  A \emph{sequoidal category} $\C$ is given by
  \begin{itemize}
    \item a symmetric monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,$ $\lunit$, $\runit$, $\sym$);
    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
      \begin{mathpar}
        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
        \and
        \run_a \from a \toisom a \sequoid I
      \end{mathpar}
      that make the diagrams
      \begin{mathpar}
        \begin{tikzcd}[column sep=31pt]
          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
            & a \sequoid (x \tensor (y \tensor z))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
            & a \sequoid (I \tensor x) \\
          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
            &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
            & a \sequoid (x \tensor I) \\
          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
      commute; and
    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
      \begin{mathpar}
        \begin{tikzcd}[column sep=30pt]
          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
            & J(a \sequoid (x \tensor y))
              &
        \end{tikzcd}
        \and
        \begin{tikzcd}
          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
            & J(a \sequoid I) \\
          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
            &
        \end{tikzcd}
      \end{mathpar}
  \end{itemize}
  \label{DefSequoidalCategory}
\end{definition}
\begin{remark}
  The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.  
  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.  
  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
\end{remark}

@@

Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
\[
  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
  \]
Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
In other words, by Proposition \ref{PropFormulaForAlpha}, $\rread$ is the composite
\[
  \rread = \oc\bN \xrightarrow{\mu_\bN} \oc\bN \tensor \oc\bN \xrightarrow{\der_\bN\tensor\oc\bN} \bN \tensor \oc\bN \xrightarrow{\wk_{\bN,\oc\bN}} \bN \sequoid\oc\bN\,.
  \]
Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
\[
  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
  \]
We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
\[
  \begin{tikzcd}
    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
      & \Varr \sequoid \oc\Varr
  \end{tikzcd}
  \]
Concretely, the strategy $\cell$ behaves as follows, as we shall prove in Proposition \ref{PropCellComb}.
When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.

@@

This coalgebraic definition of the $\cell$ strategy will be sufficient for most of our purposes, it will also be convenient to have a more direct definition.

\begin{proposition}
  The strategy $\cell$ is the strategy on $\oc\bN \implies \oc\Varr$ that behaves as follows.  
  It replies to a move $q_n$ (i.e., the initial move in the $n$-th component of $\bC$ in $\Varr$) with the unique answer $a$, and replies to the move $q$ in the $\bN$ component of $\Varr$ with that number $n$ such that $q_n$ was the most recently played $O$-move in the $\bC^\bN$ component, or, if no such move has been played, it interrogates $\oc\bN$ on the left and copies the value back on to the right.
  \label{PropCellComb}
\end{proposition}
\begin{proof}
  It will suffice to show that the strategy $\cell$ as described in the statement makes the diagram
  \[
    \begin{tikzcd}
      \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
        & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
        & \Varr \sequoid \oc\Varr
    \end{tikzcd}
    \]
  commute.
  Since $\dist_{(\bC)_\bN,\bN}$ is an isomorphism, it will suffice to show commutativity of the diagram formed by composing by it on the right; i.e.:
  \[
    \begin{tikzcd}[column sep=60pt]
      \oc\bN \arrow[rr, "{\langle (\wwrite_n)_{n\in\bN},\rread \rangle}"] \arrow[d, "\cell"']
        &
          & (\bC \sequoid\oc\bN)^\bN \times (\oc\bN \sequoid \oc\bN) \arrow[d, "(\bC \sequoid \cell)^\bN \times (\bN \sequoid \cell)"] \\
      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
        & \Varr\sequoid\oc\Varr \arrow[r, "{\dist_{(\bC)_{\bN},\bN}}"]
          & {(\bC \sequoid \oc\Varr)^{\bN} \times (\bN \sequoid \oc\Varr)\,.}
    \end{tikzcd}
    \]
  That is, we need to show that the following diagrams commute, where $n$ in the first diagram ranges over the natural numbers.
  \begin{mathpar}
    \begin{tikzcd}[column sep=40pt]
      \oc\bN \arrow[rr, "\wwrite_n"] \arrow[d, "\cell"']
        &
          & \bC \sequoid \oc\bN \arrow[d, "\bC \sequoid \cell"] \\
      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_n \sequoid \oc\Varr"]
          & \bC \sequoid \oc\Varr
    \end{tikzcd}
    \and
    \begin{tikzcd}[column sep=40pt]
      \oc\bN \arrow[rr, "\rread"] \arrow[d, "\cell"']
        &
          & \bN \sequoid \oc\bN \arrow[d, "\bN \sequoid \cell"] \\
      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_\bN \sequoid \oc\Varr"]
          & \bN \sequoid \oc\Varr
    \end{tikzcd}
  \end{mathpar}
  Consider the first diagram.  
  We may identify plays of $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q_n$ in $\Varr$ (i.e., the initial move $q$ in the $n$-th copy of $\bC$).
  We need to show that plays in $\wwrite_n;(\bC\sequoid\cell)$ take the same form.  
  Indeed, the response to the initial move in $\bC$ in $\wwrite_n;(\bC\sequoid\cell)$ is the unique response $a$, by the definition of $\wwrite_n$; thereafter, play continues in $\oc\Varr$ according to $\cell$ -- so the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played already in $\oc\Varr$, will be the most recently occurring value of $m$.

  If no $q_m$ has been played in $\oc\Varr$, then the behaviour of $\cell$ tells us that we must interrogate the $\oc\bN$ in $\bC\sequoid\oc\bN$ in order to get the value.  
  By the definition of $\wwrite_n$, the value returned will be $n$, mirroring the behaviour in $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$.

  Now consider the second diagram.  
  We may identify plays of the strategy $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q$ in $\Varr$ (i.e., the initial move $q$ in the copy of $\bN$).
  We need to show that plays in $\rread;(\bN\sequoid\cell)$ take the same form.  
  Indeed, the response to the initial move will be to interrogate $\oc\bN$ on the left to get the value.  
  Thereafter, play will continue between $\oc\bN$ and $\oc\Varr$ according to the $\cell$ strategy -- so once again the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played, will be the most recently occurring value $m$.

  If no $q_m$ has been played in $\oc\Varr$, then, by the definition of $\rread$, the strategy will interrogate $\oc\bN$ in order to get its response, just as in the strategy $\cell;\alpha_{\Varr};(\pr_\bN\sequoid\oc\Varr)$.
\end{proof}

@@

Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$.

### 2019-04-16 Thesis/pmonads.tex
Nightly commit.
Finished chapter.

\input{../common/preamble}
\begin{document}
\section{Parametric monads}

@@

\begin{remark}
  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Section \ref{SecMonads}.
\end{remark}

>>>>

\input{../common/preamble}
\begin{document}
\section{Parametric monads}
\label{ChapParametricMonads}

@@

\begin{remark}
  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Chapter \ref{ChapMonads}.
\end{remark}
